|

### 2016-06-02 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

mzid_pnnl         <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt", sep="\t", header=T)
frm_docker        <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.txt", sep="\t", header = T)

@@

```{r echo=F, cache=T, warning=F, include=F}
setwd("~/Dropbox/_SPACE/Benchmark/11")
dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfplus.mzid")
#dta_mzml  <- readMSData(files = file_mzml[2])
#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb.tsv", sep="\t", header = T)
dta       <- flatten(dta_mzid)
colnames(dta)[2] <- "Scan"

```
MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker). From `r nrow(dta)` rows, `r sum(duplicated(dta$Scan))` duplicated scan numbers were removed.

```{r echo=F}
dta <- dta[,c("Scan","ms-gf:specevalue","pepseq")]
names(dta) <- c("Scan","MSGFDB_SpecEValue","Peptide_dta")
dta_merge <- merge(x=pnnl, y=dta, by=c("Scan","MSGFDB_SpecEValue"), all.x=T)

same      <- dta_merge[(dta_merge$Peptide_dta==dta_merge$Peptide),]
same      <- same[!is.na(same$Scan),]
print(paste("Exact match:", nrow(same),"out of", nrow(pnnl)))

diff_pep <- dta_merge[(dta_merge$Peptide_dta!=dta_merge$Peptide),]
print(paste("Diff peptide:", nrow(diff_pep)))
head(diff_pep)
```

>>>>

mzid_pnnl         <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_groundtruth_fht.txt", sep="\t", header=T)
frm_docker        <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.txt", sep="\t", header = T)

@@

```{r echo=F, cache=T, warning=F, include=F}
setwd("~/Dropbox/_SPACE/Benchmark/11")
dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.mzid")
#dta_mzml  <- readMSData(files = file_mzml[2])
#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.tsv", sep="\t", header = T)
dta_flt    <- flatten(dta_mzid)
colnames(dta_flt)[2] <- "Scan"

```
MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker).

```{r echo=F}
dta <- dta_flt[,c("Scan","ms-gf:specevalue","pepseq")]
print(paste("Peptides:",nrow(dta),"with",sum(duplicated(dta$Scan)), "duplicated scan numbers."))
names(dta) <- c("Scan","MSGFDB_SpecEValue","Peptide")
dta <- dta[!duplicated(dta$Scan),]
print(paste("After removing duplicates",nrow(dta), "peptides remained."))

pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
pnnl <- pnnl[!duplicated(pnnl$Scan),]
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))

m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)

same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]

diff_spec <- m_table[(m_table$MSGFDB_SpecEValue.x !=m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]

diff_pep <- m_table[(m_table$Peptide.x != m_table$Peptide.y),]
```
